% Blockchain_contracts.tex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage{enumitem}
\title{Blockchain Smart-Contract Prompts}
\author{}
\date{}

\begin{document}
\maketitle
\tableofcontents
\vspace{1em}

% Section 1
\section{ERC20 / Fungible Tokens (Extended)}
\begin{itemize}[leftmargin=*]
  \item Create a tax token that charges 3\% on every transfer and sends the tax to the treasury wallet.
  \item Build a rebasing token whose supply adjusts every 24 hours to maintain price stability.
  \item Develop a token with time-decaying balances (balances shrink 1\% per week).
  \item Create an inflationary ERC20 token that mints 1\% of total supply every month to the treasury.
  \item Build a flash-mintable ERC20 token where users can mint tokens only within a single transaction.
  \item Create an ERC20 with quadratic mint costs (mint cost increases over time).
  \item Develop a token that locks transferred tokens for 30 days before they become spendable.
  \item Create an ERC20 token with tiered roles: minter, freezer, controller.
\end{itemize}

% Section 2
\section{ERC721 / NFT (Advanced)}
\begin{itemize}[leftmargin=*]
  \item Create an NFT with dynamic rarity: rarity changes based on user activity.
  \item Build a rental NFT system where users can rent NFTs for a fixed duration.
  \item Develop an NFT that expires after a year and becomes non-transferable.
  \item Create an NFT passport that stores user KYC hash on-chain.
  \item Build a carbon-credit NFT that burns when redeemed for carbon offsets.
  \item Develop a 3D NFT model renderer with on-chain metadata updates.
  \item Create a breeding NFT system like CryptoKitties with genetic attributes.
\end{itemize}

% Section 3
\section{ERC1155 / Multi-Asset}
\begin{itemize}[leftmargin=*]
  \item Develop a multi-token system where each item type has its own supply cap.
  \item Create an ERC1155-based crafting system where combining multiple tokens produces a new one.
  \item Build a consumable-based ERC1155 where some items are burn-to-use.
  \item Develop a dynamic drop-table reward system using ERC1155 tokens.
\end{itemize}

% Section 4
\section{DAO / Governance (Level 2)}
\begin{itemize}[leftmargin=*]
  \item Design a minimalistic DAO using quadratic voting.
  \item Create a Delegated Governance DAO where members can delegate votes to representatives.
  \item Develop a token-curated registry for ranking projects.
  \item Create a multi-branch DAO where separate councils govern different modules.
\end{itemize}

% Section 5
\section{DeFi Primitives (Advanced)}
\begin{itemize}[leftmargin=*]
  \item Build a liquidation engine for lending markets.
  \item Develop a synthetic asset protocol where users mint USD-pegged tokens using ETH collateral.
  \item Create a stablecoin with a PID controller for peg stability.
  \item Build a TWAMM (time-weighted AMM) for long-term swaps.
  \item Develop a perps (perpetual futures) contract with funding rate adjustments.
\end{itemize}

% Section 6
\section{Staking / Yield}
\begin{itemize}[leftmargin=*]
  \item Create a dual-staking contract where users earn rewards in two different tokens.
  \item Develop auto-compounding staking that compounds rewards into principal.
  \item Build a staking contract with slashing for early withdrawals.
  \item Create NFT-based staking where rewards depend on NFT rarity.
\end{itemize}

% Section 7
\section{Marketplace / Commerce v2}
\begin{itemize}[leftmargin=*]
  \item Create a decentralized ticketing platform with anti-bot minting verification.
  \item Develop a cross-collection NFT aggregator marketplace.
  \item Build a 'fair Dutch auction' smart contract for art collections.
  \item Create a subscription billing smart contract with auto-renew logic.
\end{itemize}

% Section 8
\section{Escrow / Custody}
\begin{itemize}[leftmargin=*]
  \item Build a hashed time-lock escrow contract for cross-chain payments (HTLC).
  \item Create a multi-item escrow where buyers can release items individually.
  \item Develop a two-party arbitration contract with vote-based dispute resolution.
\end{itemize}

% Section 9
\section{Access Control \& Compliance}
\begin{itemize}[leftmargin=*]
  \item Develop an ERC20 that restricts transfers only to KYC-approved addresses.
  \item Create a geo-fenced token sale blocking restricted countries.
  \item Build a multi-admin system with weighted permission levels.
  \item Create a role that can freeze or unfreeze individual accounts.
\end{itemize}

% Section 10
\section{Oracle-Integrated Contracts}
\begin{itemize}[leftmargin=*]
  \item Build a temperature-based insurance payout triggered by Chainlink weather oracle.
  \item Create a gas-price hedging contract using oracle-reported base fees.
  \item Develop an on-chain reputation index updated through an oracle feed.
\end{itemize}

% Section 11
\section{Cross-Chain / Interoperability}
\begin{itemize}[leftmargin=*]
  \item Create a bridge contract that locks tokens on chain A and mints wrapped tokens on chain B.
  \item Develop an omnichain NFT that moves between networks using LayerZero.
  \item Build a cross-chain message dispatcher contract.
\end{itemize}

% Section 12
\section{Soulbound Tokens / Identity}
\begin{itemize}[leftmargin=*]
  \item Create a non-transferable SBT that records a user's credentials.
  \item Develop a university degree SBT with revoking capability.
  \item Build a reputation score SBT that increments after verified actions.
\end{itemize}

% Section 13
\section{Account Abstraction (ERC-4337)}
\begin{itemize}[leftmargin=*]
  \item Create a smart account contract with spending limits.
  \item Develop a user wallet contract that supports session keys.
  \item Build a multi-owner smart wallet with timelocked operations.
\end{itemize}

% Section 14
\section{Zero-Knowledge Friendly}
\begin{itemize}[leftmargin=*]
  \item Create a zk-verifiable credential NFT where metadata is a hash commitment.
  \item Develop a contract that verifies ZK-SNARK proofs before minting.
  \item Build a voting contract where votes are anonymous via ZK proofs.
\end{itemize}

% Section 15
\section{Advanced Utility Contracts}
\begin{itemize}[leftmargin=*]
  \item Create a rate-limited token vault allowing withdrawals once every 24 hours.
  \item Develop a Commit-Reveal scheme for random number generation.
  \item Build a verifiable lottery with automated payout distribution.
\end{itemize}

% Section 16
\section{Payment Protocols}
\begin{itemize}[leftmargin=*]
  \item Create a payment splitter contract that divides incoming funds among multiple recipients.
  \item Develop a streaming payment contract (Superfluid-style).
  \item Build a pay-per-use API metering contract with credits.
\end{itemize}

% Section 17
\section{AI/Autonomous Agent Contracts}
\begin{itemize}[leftmargin=*]
  \item Create an autonomous trading bot contract that rebalances weekly.
  \item Build an on-chain agent that executes tasks when gas prices drop.
  \item Develop an AI-oracle-governed treasury allocator.
\end{itemize}

% Section 18
\section{SocialFi / Community Contracts}
\begin{itemize}[leftmargin=*]
  \item Create a follower-based token airdrop system.
  \item Develop a tipping contract for microtransactions among creators.
  \item Build a group wallet requiring majority approval for spending.
\end{itemize}

% Section 19
\section{Gaming / Metaverse}
\begin{itemize}[leftmargin=*]
  \item Create an on-chain XP leveling system for player profiles.
  \item Develop a loot-box RNG system for game rewards.
  \item Build an avatar equipment system with composable NFTs.
\end{itemize}

% Section 20
\section{Insurance Protocols}
\begin{itemize}[leftmargin=*]
  \item Create a parametric insurance contract for crop failures.
  \item Develop a staking-backed insurance pool.
  \item Build an NFT-based insurance certificate that is transferable.
\end{itemize}

% Section 21
\section{Misc / Hybrid}
\begin{itemize}[leftmargin=*]
  \item Create a multisig vault that requires biometrics via oracle before signing.
  \item Develop a token-bound smart wallet for ERC6551 NFTs.
  \item Create a rent-to-own contract where users gradually gain token ownership.
  \item Build a mining reward contract where difficulty adjusts automatically.
  \item Develop a vote-escrowed token (veToken) with lockup-based voting weight.
  \item Create an NFT that unlocks ERC20 tokens at each milestone.
  \item Build a decentralized pledge contract for fundraising goals.
  \item Create a digital will contract that transfers assets on inactivity.
  \item Develop a charity donation router tracking donor history.
\end{itemize}

% Footer: export options
\section*{Export / Conversion Options}
\begin{itemize}[leftmargin=*]
  \item JSON array
  \item CSV
  \item Markdown
  \item Training dataset for your LLM
  \item Tags by category
  \item Difficulty score
  \item Contract complexity score
\end{itemize}

\end{document}
